Spike spectra for recurrences

### 2022-08-03 Manuscript/inter_spike_manuscript_mdpi.tex
last comment

The signal, which we would like to transform is decomposed into a set of appropriate basis functions.\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
such time series are often spiky, which favors the proposed decomposition technique. But the proposed method can be applied to any sort of signal.} Instead of using trigonometric 
functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 
$t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
vector $\bf{s}$. 
First, $\tilde{N}$ different DC's of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,\tilde{N}]$ and $\tilde{N}=\ceil*{N/2}+1$. Second, in order to account 
for possible phase shifts of 
these basis functions occurring in $\bf{s}$, each of these $\tilde{N}$ different DC's also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
$M = \sum_{i=1}^{\tilde{N}}i$ 
basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure)
\begin{align}
\label{eq_basis_matrix} \bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
\label{eq_T_is} T_\text{is}(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
\end{align}
\todo[inline]{Make Eq.\eqref{eq_T_is} nicer}
Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
Furthermore, there will be identical basis functions and also basis functions, which do not allow for an unambiguous inter spike period, 
if we would include all $N$ possible inter spike periods for a signal of length $N$ instead of $\ceil*{N/2}+1$ (Fig.~\ref{fig_tau_rr_basis_functions}A). 
The reason is that in contrast to a trigonometric decomposition, where the Nyquist frequency marks a lower bound for the corresponding wave period, here 
the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$ (schematically illustrated in 
Fig.~\ref{fig_tau_rr_basis_functions}B).\\

>>>>

The signal, which we would like to transform is decomposed into a set of appropriate basis functions.\footnote{We focus on $\tau$-RR in this article, Eq.~\eqref{eq_tau_rr}, since 
such time series are often spiky, which favors the proposed decomposition technique. But the proposed method can be applied to any sort of signal.} Instead of using trigonometric 
functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 
$t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
vector $\bf{s}$. 
First, $\tilde{N}$ different DC's of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,\tilde{N}]$ and $\tilde{N}=\ceil*{N/2}+1$. Second, in order to account 
for possible phase shifts of 
these basis functions occurring in $\bf{s}$, each of these $\tilde{N}$ different DC's also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
$M = \sum_{i=1}^{\tilde{N}}i$ 
basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
(Fig.~\ref{fig_tau_rr_basis_functions} illustrates the described procedure)
\begin{align}
\label{eq_basis_matrix} \bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
\label{eq_T_is} T_\text{is}(i)&= n \quad,~s.t.~~ n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
\end{align}
\todo[inline]{HK: Eq.\eqref{eq_basis_matrix} is somehow ugly. Maybe someone can get rid of that sum and make it nicer? I tried with 
modulo, but just could not figure it out exactly. There must be an easy way I do not see.}
Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
Furthermore, there will be identical basis functions and also basis functions, which do not allow for an unambiguous inter spike period, 
if we would include all $N$ possible inter spike periods for a signal of length $N$ instead of $\ceil*{N/2}+1$ (Fig.~\ref{fig_tau_rr_basis_functions}A). 
The reason is that in contrast to a trigonometric decomposition, where the Nyquist frequency marks a lower bound for the corresponding wave period, here 
the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$ (schematically illustrated in 
Fig.~\ref{fig_tau_rr_basis_functions}B).\\
